Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-15 doc/GMP2015/s02_preliminaries.tex
Clean up + changes to preliminaries.

\section{Preliminaries}

@@

% A paragraph of preliminaries such as rigidity matrix R, stress vectors S one coordinate per edge (w/ SR =E (external stress vector, 2 coordinates  per vertex)); flex vectors F (2 coordinates per vertex) (right nullspace/kernel of R) should precede the definition of independent, overconstrained (not independent), rigid (contains an independent set with sufficiently many eedges/constraints) isostatic (wellconstrained/minimally rigid), , flexible (not rigid), underconstrained (independent and not rigid).

% After that, define DR plans etc.

@@

\begin{definition}
    A graph is \textbf{independent} (or \textbf{sparse}) if \todo{define}.
\end{definition}

\begin{definition}
    A graph is \textbf{over-constrained} if, given constant $k$, there exists some induced subgraph $S\subseteq G$ such that $d(S) > k$.
\end{definition}

\begin{definition}
    A graph is \textbf{well-constrained} if, given constant $k$, $d(G) = k$ and for all induced subgraphs $S\subseteq G$, (1) $d(S)\leq k$, or (2) given a set of trivial graphs $T$, $S$ is isomorphic to one of the graphs in $T$ (i.e.\ $S$ is trivial).
\end{definition}

@@

\begin{definition}
    A graph is \textbf{under-constrained} if, given constant $k$, $G$ is not rigid.
\end{definition}

@@

\begin{definition}
    The \textbf{decomposition-recombination (DR-) plan} of graph $G$, $DRP(G)$, is defined as a tree that has the following properties:
    \begin{enumerate}
        \item The root of the tree `contains' $G$.
        \item For all nodes, $C$, that `contain' nontrivial graphs, its $N$ children, $C_1, \ldots, C_N$, are trivial or well-constrained vertex-maximal proper subgraphs of that node $C$.
        \item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
        \item A node with a trivial subgraph is a leaf.
    \end{enumerate}

>>>>

\section{Preliminaries}\label{prelim}

@@

% A paragraph of preliminaries such as:
%     - rigidity matrix R,
%     - stress vectors S one coordinate per edge (w/ SR =E (external stress vector, 2 coordinates  per vertex));
%     - flex vectors F (2 coordinates per vertex) (right nullspace/kernel of R)
% Should precede the definition of
%     + independent,
%     + overconstrained (not independent),
%     - rigid (contains an independent set with sufficiently many eedges/constraints)
%     - isostatic (wellconstrained/minimally rigid), ,
%     - flexible (not rigid),
%     + underconstrained (independent and not rigid).
% After that, define DR plans etc.

@@

\begin{definition}
    A graph is \textbf{independent} (or \textbf{sparse}) if, given constant $k$, for all non-trivial subgraphs $S\subseteq G$, $d(S) \leq k$.
\end{definition}

% \begin{definition}
%     A graph is \textbf{over-constrained} if, given constant $k$, there exists some
%     % induced
%     subgraph $S\subseteq G$ such that $d(S) > k$.
% \end{definition}

\begin{definition}
    A graph is \textbf{over-constrained} if it is not independent.
\end{definition}

% \begin{definition}
%     A graph is \textbf{well-constrained} if, given constant $k$, $d(G) = k$ and for all
%     % induced
%     subgraphs $S\subseteq G$, (1) $d(S)\leq k$, or (2) given a set of trivial graphs $T$, $S$ is isomorphic to one of the graphs in $T$ (i.e.\ $S$ is trivial).
% \end{definition}

\begin{definition}
    A graph is \textbf{well-constrained} (or \textbf{tight}) if, given constant $k$, $G$ is independent and $d(G)=k$.
\end{definition}

@@

\begin{definition}
    A graph is \textbf{under-constrained} if $G$ is independent and not rigid.
\end{definition}

@@

\begin{definition}
    The \textbf{decomposition-recombination (DR-) plan} of graph $G$, $DRP(G)$, is defined as a tree that has the following properties:
    \begin{enumerate}
        \item The root of the tree `contains' $G$.
        \item For all nodes, $C$, that `contain' non-trivial graphs, its $N$ children, $C_1, \ldots, C_N$, are trivial or well-constrained vertex-maximal proper subgraphs of that node $C$.
        \item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
        \item A node with a trivial subgraph is a leaf.
    \end{enumerate}

### 2014-12-15 doc/GMP2015/s03_drp.tex
Clean up + changes to preliminaries.

% We develop this notion of the canonical optimal DR-plan by carefully considering the case of a union of any two nontrivial well-constrained vertex-maximal proper subgraphs of a well-constrained graph. By definition, any subgraph of a well-constrained graph will either be (1) trivial, (2) under-constrained, or (3) well-constrained. We will analyze all 3 possibilities in turn. These observations will lead to interesting properties that govern the behavior of optimal DR-plans on well-constrained graphs.

% We show this by carefully considering all of the potential cases of the unions of subgraphs. By definition, any subgraph of a well-constrained graph will either be (1) under-constrained, (2) well-constrained, or (3) trivial. We will analyze all 3 possibilities in turn, in the case of a union of any two nontrivial well-constrained vertex-maximal proper subgraphs.

@@

% In the forward direction: From Lemma \ref{uc-l1}, the intersection cannot be trivial. The intersection also cannot be under-constrained. If $F_i \cap F_j$ were under-constrained, then for $F_i$ to be well-constrained you would need to add more constraints (edge weight) than degrees of freedom (vertex weight) to the intersection. The same is true for $F_j$. If both of these were satisfied, then the union of $F_i$ and $F_j$ would result in an over-constrained nontrivial graph. This is a contradiction, by definition of a well-constrained graph. Therefore, the intersection can only be well-constrained.

@@

In figure \ref{doublets}, the two well-constrained vertex-maximal proper subgraphs of the graph are the two doublets, shown in the second level of the DR-plan. These intersect on the well-constrained graph $\{b_1,b_2,b_3\}$. This will necessarily be a child $N=2$ levels below the parent of the two doublets, as explained in Theorem \ref{wc-t1}. Also shown is the decomposition of the individual doublets. These have five well-constrained vertex-maximal proper subgraphs, the two triangles and the three edges connecting them. As explained in Theorem \ref{uc-t1}, all of them must be included in the optimal DR-plan. Were any left out, the union of the children would not be the entire parent.

@@

In figure \ref{c2c3ofk33s}... \todo{Is it worth working through this? The first example has trivial and non-trivial.}

>>>>

% We develop this notion of the canonical optimal DR-plan by carefully considering the case of a union of any two non-trivial well-constrained vertex-maximal proper subgraphs of a well-constrained graph. By definition, any subgraph of a well-constrained graph will either be (1) trivial, (2) under-constrained, or (3) well-constrained. We will analyze all 3 possibilities in turn. These observations will lead to interesting properties that govern the behavior of optimal DR-plans on well-constrained graphs.

% We show this by carefully considering all of the potential cases of the unions of subgraphs. By definition, any subgraph of a well-constrained graph will either be (1) under-constrained, (2) well-constrained, or (3) trivial. We will analyze all 3 possibilities in turn, in the case of a union of any two non-trivial well-constrained vertex-maximal proper subgraphs.

@@

% In the forward direction: From Lemma \ref{uc-l1}, the intersection cannot be trivial. The intersection also cannot be under-constrained. If $F_i \cap F_j$ were under-constrained, then for $F_i$ to be well-constrained you would need to add more constraints (edge weight) than degrees of freedom (vertex weight) to the intersection. The same is true for $F_j$. If both of these were satisfied, then the union of $F_i$ and $F_j$ would result in an over-constrained non-trivial graph. This is a contradiction, by definition of a well-constrained graph. Therefore, the intersection can only be well-constrained.

@@

\begin{example}
    In figure \ref{doublets}, the two well-constrained vertex-maximal proper subgraphs of the graph are the two doublets, shown in the second level of the DR-plan. These intersect on the well-constrained graph $\{b_1,b_2,b_3\}$. This will necessarily be a child $N=2$ levels below the parent of the two doublets, as explained in Theorem \ref{wc-t1}. Also shown is the decomposition of the individual doublets. These have five well-constrained vertex-maximal proper subgraphs, the two triangles and the three edges connecting them. As explained in Theorem \ref{uc-t1}, all of them must be included in the optimal DR-plan. Were any left out, the union of the children would not be the entire parent.
\end{example}

@@

\begin{example}
    In figure \ref{c2c3ofk33s}... \todo{Is it worth working through this? The first example has trivial and non-trivial.}
\end{example}

### 2014-12-15 doc/GMP2015/s07_problempinning.tex
Added more to Problem pinning
Clean up + changes to preliminaries.

We can use DR plans to help in solving questions in designs for graphene and silica bilayers (\textcolor{red}{Add Citation}). Specifically, we will look into the problem when you have a monolayer and it is underconstrained. To make this thing isostatic, there are a few methods we can apply.

@@

\begin{defintion}
    A body-pin qusec is a multi-body-pin qusec with the following conditions:
    \begin{itemize}
        \item Each pin is shared by at most 2 bodies
        \item No 2 bodies share more than one pin 
    \end{itemize}
    Such a body-pin qusec can also be seen as a {\em body-bar qusec} where the bodies are the original bodies and each pin represents 2 bars from one body to another. For such body-bar qusecs, graphs with 1 and 2 dofs can be characterized by being $(3,4)$ and $(3,5)$ tight respectively.
\end{defintion}

@@

\begin{defnition}
    A $(k,l)$ tight DR plan is one in which each child node is either a vertex maximal proper $(k,l)$ tight subgraph of the parent node or it is trivial. In our case, the trivial nodes are just the bodies. 
\end{defnition}

@@

\begin{proof}
    \textcolor{red}{Item 1 Follows from paper?}

@@

%TODO write out the stuff for 2 dof

>>>>

We can use DR plans to help in solving questions in designs for graphene and silica bilayers (\todo{Add Citation}). Specifically, we will look into the problem when you have a monolayer and it is underconstrained. To make this thing isostatic, there are a few methods we can apply.

@@

\begin{definition}
    A body-pin qusec is a multi-body-pin qusec with the following conditions:
    \begin{itemize}
        \item Each pin is shared by at most 2 bodies
        \item No 2 bodies share more than one pin
    \end{itemize}
    Such a body-pin qusec can also be seen as a {\em body-bar qusec} where the bodies are the original bodies and each pin represents 2 bars from one body to another. For such body-bar qusecs, graphs with 1 and 2 dofs can be characterized by being $(3,4)$ and $(3,5)$ tight respectively.
\end{definition}

@@

\begin{definition}
    A $(k,l)$ tight DR plan is one in which each child node is either a vertex maximal proper $(k,l)$ tight subgraph of the parent node or it is trivial. In our case, the trivial nodes are just the bodies.
\end{definition}

@@

\begin{proof}
    \todo{Item 1 Follows from paper?}

@@
